\input basic
\font L=cml10 \font M=cml12 \font N=cmss8 \font R=CMR10 \font I=CMI10
\font A=CMASC10 \font X=CUL30
\output{\vbox to size{\page\vfill}} % No page numbers, please.
\parindent 0pt
\vskip 0.5in
\par
\hbox to size{\hbox{\vbox{\vfill
 \hbox{\:MColumbia University \:Lin the City of New York}
 \vskip 0.1in
 \hbox{\:NCENTER FOR COMPUTING ACTIVITIES}
 \hbox{612 West 115th Street}
 \hbox{New York, N.Y. 10025}
 \hbox{(212) 280-3703}
}}\hss\vbox{\hbox{\hss\:Xb}\vfill\hbox{\hss\:IJune 6, 1985}}}
\parskip 12pt\vskip .25in
\:R
Dear Kermit User,

Included on the enclosed tape are all the successful implementations of Kermit
done or received by us to date, in the category that you ordered.  Your tape
includes source files and documentation, plus binaries when practical.  Also
included is a file called {\:AATAPE.HLP}, which describes the contents of
the tape in more detail.  That file is also enclosed on paper; please read it
to find out how to find the Kermit implementations you want.

Kermit is a voluntary effort.  Although the Kermit protocol was designed by us
at Columbia and many of the Kermit programs were written by us, the majority of
programs were contributed from elsewhere.  In many cases, we have no way to
test these contributed programs, and cannot always attest to their quality.
However, we do not distribute Kermit programs that we know to be inoperable, or
for which source code is not provided.  When bugs are found or functionality is
missing, you are most welcome to make any desired changes.

The popularity of Kermit has been far greater than we ever expected, and we
have been shipping nearly ten tapes per day over the past year, and the demand
continues to rise.  The 100 dollar-per-tape distribution fee which has been in
effect since May 1983 has helped us keep up with the demand by hiring part-time
students to help fill the orders.

The software, sources, and documentation remain free.  Kermit is distributed in
this manner with the understanding that it will never be sold as a product,
{\:Iper se}.  This is done in the hope that use of Kermit will become
widespread enough to make communications between any two computers a real
possibility rather than a pipedream.  We encourage you to return any new
implementations, bug fixes, or documentation to us so we can pass them along to
others.  We also encourage you to pass Kermit along directly to other sites
that ask you about it, rather than referring them back to us.  We only ask that
profit not be your motive, credit be given where it is due, and that new
material be sent back to us so that we can maintain a definitive and
comprehensive set of Kermit implementations.  I've attempted to clarify these
points for commercial sites in some detail in an enclosed flyer on commercial
use and distribution of Kermit; please consult it if you have any doubts.

Meanwhile, new implementations of Kermit are under development and old ones are
being improved.  This is a continuous process.  If you are interested in new
developments, feel free to give a call in a few months.  And finally, PLEASE
USE KERMIT ONLY FOR PEACEFUL PURPOSES.
\par\vskip 20pt
\hbox to size{{\hskip 3.5in}Sincerely,}
\vskip 30pt
\hbox to size{{\hskip 3.5in}Frank da Cruz\hss}
\hbox to size{{\hskip 3.5in}Manager of System Integration\hss}
\par\vfill
\end
